### 2020-05-01 system-model.tex
:art: Improve format
:pencil: Alternating optimization

		To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
		\begin{equation}
			\begin{split}
				{h_{n_1}^*}{h_{n_2}}
				&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
				&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
				&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
				&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
			\end{split}
		\end{equation}
		where
		\begin{equation}
			\boldsymbol{R}_{n_1,n_2}=
			\begin{bmatrix}
				\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
				h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
			\end{bmatrix}
		\end{equation}
		On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries. It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}. Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_su}.
		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_k_su}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}\left(2\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H\right)\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
				\end{split}
			\end{equation}
		\end{figure*}

@@

		which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
		% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
		% \begin{equation}
		% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
		% \end{equation}
		% where the equality holds if and only if the direct and IRS-aided links align with each other. In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$. Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
		% \begin{equation}
		% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
		% \end{equation}
		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
		% \begin{equation}\label{eq:phi_n}
		% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
		% \end{equation}

>>>>

		% ? AO: optimize phase shifts with given weights
		Define waveform matrices $\boldsymbol{M}_I=\boldsymbol{w}_I^*\boldsymbol{w}_I^T$ and $\boldsymbol{M}_P=\boldsymbol{w}_P^*\boldsymbol{w}_P^T$. Also, let $\boldsymbol{M}_{I/P, n}$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}_{I/P}$ and nulls the remaining entries. It holds that $\boldsymbol{M}_{I/P,0} \succeq 0$ and $\boldsymbol{M}_{I/P,-n}=\boldsymbol{M}_{I/P,n}^H$ for $n{\ne}0$ \cite{Huang2017}. Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_phase}.
		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_k_phase}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h}+\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})\\
					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{I,n}\boldsymbol{h})^H+(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,n}\boldsymbol{h})^H}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{h}^H\boldsymbol{M}_{I,0}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{M}_{P,0}\boldsymbol{h})}
				\end{split}
			\end{equation}
		\end{figure*}

		% ? AO: optimize weights with given phase shifts
		To tackle the non-convex current constraint, we introduce a channel matrix $\boldsymbol{M}=\boldsymbol{h}^*\boldsymbol{h}^T \in \mathbb{C}^{N \times N}$ whose $(n_1,n_2)$ entry equals
		\begin{equation}
			\begin{split}
				{h_{n_1}^*}{h_{n_2}}
				&=(h_{D,n_1}^*+\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*)(h_{D,n_2}+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*})\\
				&={h_{D,n_2}}{h_{D,n_1}^*}+{h_{D,n_2}}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}h_{D,n_1}^*+\boldsymbol{v}^T{\boldsymbol{\Phi}_{n_2}^*}\boldsymbol{\Phi}_{n_1}^T\boldsymbol{v}^*\\
				&=\bar{\boldsymbol{v}}^T\boldsymbol{R}_{n_1,n_2}\bar{\boldsymbol{v}}^*\\
				&=\mathrm{Tr}(\boldsymbol{R}_{n_1,n_2}\boldsymbol{V}^*)
			\end{split}
		\end{equation}
		where
		\begin{equation}
			\boldsymbol{R}_{n_1,n_2}=
			\begin{bmatrix}
				\boldsymbol{\Phi}_{n_2}^*\boldsymbol{\Phi}_{n_1}^T & \boldsymbol{\Phi}_{n_2}^*{h_{D,n_1}^*} \\
				h_{D,n_2}{\boldsymbol{\Phi}_{n_1}^T}               & h_{D,n_2}{h_{D,n_1}^*}
			\end{bmatrix}
		\end{equation}
		On top of this, $\boldsymbol{M}_n$ keeps the $n$-th ($n=-N+1,\dots,N-1$) diagonal of $\boldsymbol{M}$ and nulls the remaining entries. It holds that $\boldsymbol{M}_0 \succeq 0$ and $\boldsymbol{M}_{-n}=\boldsymbol{M}_{n}^H$ for $n{\ne}0$ \cite{Huang2017}. Therefore, \ref{eq:z_k_truncated} is transformed to \ref{eq:z_k_waveform}.
		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_k_waveform}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I+\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)\\
					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					% &\quad+\frac{3}{4}{k_4}{\rho^2}{R_{\text{ant}}^2}\left({\boldsymbol{w}_I^H\boldsymbol{M}_n}\boldsymbol{w}_I({\boldsymbol{w}_I^H\boldsymbol{M}_0}\boldsymbol{w}_I)^H+{\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P({\boldsymbol{w}_P^H\boldsymbol{M}_0}\boldsymbol{w}_P)^H\right)
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{n=-N+1}^{N-1}{2(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{M}_n\boldsymbol{w}_I)^H+(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{M}_n\boldsymbol{w}_P)^H}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}{(\boldsymbol{w}_I^H\boldsymbol{M}_0\boldsymbol{w}_I)(\boldsymbol{w}_P^H\boldsymbol{M}_0\boldsymbol{w}_P)}
				\end{split}
			\end{equation}
		\end{figure*}
		We then introduce auxiliary vectors $\boldsymbol{t}_{I/P}=[t_{{I/P},0},\dots,t_{{I/P},N-1}]^T \in \mathbb{C}^{N \times 1}$ with $t_{{I/P},n}=\boldsymbol{w}_{I/P}^H\boldsymbol{M}_n\boldsymbol{w}_{I/P}=\mathrm{Tr}(\boldsymbol{M}_n\boldsymbol{W}_{I/P})$ and transform \ref{eq:z_k_waveform} to
		% and define coefficient matrix $\boldsymbol{A}_0=\mathrm{diag}\{\}$
		\begin{equation}\label{eq:z_k_su_compact}
			\begin{split}
				z
				&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}(t_{I,0}+t_{P,0})\\
				&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}(4\boldsymbol{t}_I^H\boldsymbol{t}_I+2\boldsymbol{t}_P^H\boldsymbol{t}_P-2t_{I,0}t_{I,0}^*-t_{P,0}t_{P,0}^*)\\
				&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}t_{I,0}t_{P,0}
			\end{split}
		\end{equation}

@@

		% which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
		% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
		% \begin{equation}
		% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
		% \end{equation}
		% where the equality holds if and only if the direct and IRS-aided links align with each other. In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$. Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
		% \begin{equation}
		% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
		% \end{equation}
		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_truncated} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
		% \begin{equation}\label{eq:phi_n}
		% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
		% \end{equation}
